---
title: "UNH2DES-README"
author: "Erik.Leppo@tetratech.com"
date: "`r Sys.time()`"
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE
                      , collapse = TRUE
                      , comment = "#>"
                      , fig.path = "README-")

```

```{r, echo = FALSE}
cat(paste0("Last Update: ",Sys.time()))
```
# UNH2DES
Translate lake data from University of New Hampshire (UNH) lab to New Hampshire Department of Environmental Services (DES) Environmental Monitoring Database (EMD).

# Badges
to come later

# Installation
To install the current version use the code below to install from GitHub. The 
use of “force = TRUE” ensures the package is installed even if already present. 
If the package `remotes` is missing the code below will install it.

```{r Install, eval=FALSE}
if(!require(remotes)){install.packages("remotes")}  #install if needed
install_github("leppott/UNH2DES", force=TRUE)
```

# Purpose
To aid users in the migration of data from UNH to DES (EMD).

# Usage

# Shiny
No plans for a Shiny app at the current time.
